---
title: "Introduction"
author: "Farhad Salimi"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tibble)
library(knitr)
library(dplyr)
library(forcats)
library(ggplot2)
library(modelr)
library(tidyr)
library(registryr)
library(scales)
```

## Overview

`registryr` provides tools for the analysis of the clinical registry datasets. These tools will be described in this vignette.

## Funnel plots
Funnel plot is a visual representation of how individual medical units (e.g. hospitals) perform compared to their peers and the overall average. It also helps to identify the outliers (i.e the ones who are performing better or worse than the average).
The `stat_funnelcount` and `stat_funnelcontinuous` functions provide easy options to add funnels to an existing ggplot.

Let's firstly load a fake dataset which comes with the package.

```{r make a simulated datasset}
data(fake_data)

head(fake_data)
```

We will use the average mortality rate and length of dtay as the benchmarks and will then make funnel plots using the `stat_funnelcount` and `stat_funnelcontinuous` functions.

```{r make the funnel plots, fig.width = 7, fig.height = 4}
n_sites <- fake_data %>% pull(site_id) %>% n_distinct()

benchmark_mortality <-
  fake_data %>%
  summarise(benchmark = sum(dead) / n()) %>%
  pull(benchmark)

fake_data_grouped <-
  fake_data %>%
  group_by(site_id) %>%
  summarise(n_deaths = sum(dead),
            mean_los = mean(los),
            n = n())

fake_data_grouped <-
  fake_data_grouped %>%
  mutate(death_rate = n_deaths / n,
         site_id = as_factor(site_id)) %>%
  # we need to manually change the denominator for the funnel plots, to make it look nicer :)
  mutate(n = seq(100, 2000, length.out = n_sites),
         sd_los = rpois(dplyr::n(), 5))

fake_data_grouped %>%
  ggplot(aes(x = n, y = death_rate)) +
  geom_hline(yintercept = benchmark_mortality,
             col = "dark blue") +
  geom_point() +
  stat_funnelcount(fill = "dark blue",
              alpha = 0.5,
              ci_limits = 0.95)+
  stat_funnelcount(fill = "light blue",
              alpha = 0.5,
              ci_limits = 0.998) +
  geom_point() +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(0, 1),
                     labels = percent_format()
                     ) +
  coord_cartesian(ylim = c(0, NA),
                  xlim = c(0, NA)) +
  theme_bw() +
  labs(
    x = "Number of surgeries",
    y = "Mortality rate"
  )

benchmark_los <-
  fake_data %>%
  summarise(benchmark = mean(los)) %>%
  pull(benchmark)

fake_data_grouped %>%
  ggplot(aes(x = n, y = mean_los, sd = sd_los)) +
  geom_hline(yintercept = benchmark_los,
             col = "dark blue") +
  stat_funnelcontinuous(fill = "dark blue",
              alpha = 0.5,
              ci_limits = 0.95) +
  stat_funnelcontinuous(fill = "light blue",
              alpha = 0.5,
              ci_limits = 0.998) +
  scale_y_continuous(expand = c(0, 0),
                     limits = c(35, 48),
                     ) +
  geom_point() +
  labs(
    x = "Number of surgeries",
    y = "Mean length of stay (days)"
  ) +
  theme_bw()

```

## Stepwise model selection
Let's find out what model we should use to adjust the outcome, we can do that by using the `stepwise` function
```{r}
model_mortality <-
  stepwise(out_var = "dead",
         ind_var = c("sex_cat", "age"),
         data = fake_data,
         model = "logistic")

mortality_adj_vars <- labels(terms(formula(model_mortality)))
```

```{r}
model_los <-
  stepwise(out_var = "los",
         ind_var = c("sex_cat", "age"),
         data = fake_data,
         model = "linear")

los_adj_vars <- labels(terms(formula(model_mortality)))
```

Now, let's risk adjust the data using the models found using the stepwise function. We can apply risk adjustment by `risk_adj` function.
```{r risk adjustment}
fake_data <- 
  fake_data %>%
  ungroup() %>%
  drop_na(sex, age)

risk_adjust(data = fake_data, 
            site_id = "site_id",
            outcome = "dead",
            outcome_type = "binary",
            adj_vars = mortality_adj_vars)

risk_adjust(data = fake_data, 
            site_id = "site_id",
            outcome = "los",
            outcome_type = "continuous",
            adj_vars = los_adj_vars)
```




